# Correlation in the estimated values of semantic association accross embedding models

# Correlations between predictors (lp and sem)

```{r}
library(tidytable)
library(dplyr)
library(stringr)
library(ggplot2)
library(reshape2)

setwd("experiment3")
```

## Read data
```{r}
data_path <- file.path("..", "experiment2", "results")

tanner_df <- read.csv(file.path(data_path, "tanner_semantic_association.csv")) |>
    filter(Acceptability == "Gram") |>
    mutate(full_implementation = paste(implementation, model, sep = "_")) |>
    group_by(implementation, model) |>
    mutate(s_sem = scale(semantic_association)) |>
    ungroup()

ucl_df <- read.csv(file.path(data_path, "ucl_semantic_association.csv")) |>
    mutate(full_implementation = paste(implementation, model, sep = "_")) |>
    group_by(implementation, model) |>
    mutate(s_sem = scale(semantic_association)) |>
    ungroup()

derco_df <- read.csv(file.path(data_path, "derco_semantic_association.csv")) |>
    mutate(full_implementation = paste(implementation, model, sep = "_")) |>
    group_by(article_n, full_implementation) |>
    mutate(
        context_length = ifelse(str_detect(implementation, "sentences1"), "Sentence(N=1)", "All")
    ) |>
    ungroup() |>
    group_by(full_implementation) |>
    mutate(s_sem = scale(semantic_association)) |>
    ungroup()

# content words pos tags
content_pos <- c("NOUN", "VERB", "ADJ", "ADV")
```

## Correlations: Tanner
all words
```{r}
cor_matrix <- tanner_df |>
    select(id, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)

cor_matrix
```

```{r}
melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

only content words
```{r}
cor_matrix <- tanner_df |>
    filter(pos %in% content_pos) |>
    select(id, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)

cor_matrix
```

```{r}
melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
    ) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

by POS tag (only content words)
```{r}
n <- 1

cor_matrix <- tanner_df |>
    filter(pos == content_pos[n]) |>
    select(id, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)


melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
    ) +
    labs(x = "", y = "", fill = "Correlation", title = content_pos[n]) +
    theme(aspect.ratio = 1)
```

## Correlations: UCL
all words
```{r}
cor_matrix <- ucl_df |>
    select(id, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)

cor_matrix
```

```{r}
melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

only content words
```{r}
cor_matrix <- ucl_df |>
    filter(pos %in% content_pos) |>
    select(id, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)

cor_matrix
```

```{r}
melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
    ) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

by POS tag (only content words)
```{r}
n <- 1

cor_matrix <- ucl_df |>
    filter(pos == content_pos[n]) |>
    select(id, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)


melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
    ) +
    labs(x = "", y = "", fill = "Correlation", title = content_pos[n]) +
    theme(aspect.ratio = 1)
```

## Correlations: DERCo
all words
```{r}
cor_matrix <- derco_df |>
    filter(context_length == "All") |>
    select(article_n, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)

cor_matrix
```

```{r}
melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

only content words
```{r}
cor_matrix <- derco_df |>
    filter(context_length == "All") |>
    filter(pos %in% content_pos) |>
    select(article_n, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)

cor_matrix
```

```{r}
melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
    ) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

by POS tag (only content words)
```{r}
n <- 1

cor_matrix <- derco_df |>
    filter(context_length == "All") |>
    filter(pos == content_pos[n]) |>
    select(article_n, word_n, semantic_association, full_implementation) |>
    pivot_wider(
        names_from = full_implementation,
        values_from = semantic_association,
        names_prefix = "semantic_association_"
    ) |>
    select(starts_with("semantic_association")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^semantic_association_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)


melted <- melt(cor_matrix)

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
    ) +
    labs(x = "", y = "", fill = "Correlation", title = content_pos[n]) +
    theme(aspect.ratio = 1)
```

