# Inspect context embeddings by looking at similar words
# NB: You must run src/context_embedding.py and src/create_context_plotting_df.py first!

```{r}
library(tidytable)
library(ggplot2)
library(ltc)

setwd("experiment3")
```

## plot top five
Read data
```{r}
df <- read.csv(file.path("results", "top_n_context_embedding_similarities.csv")) |>
    group_by(model, implementation, id, word_n) |>
    mutate(
        "similarity_rank" = factor(min_rank(desc(cosine_similarity)))
    )
```

```{r}
models <- df |>
    pull(model) |>
    unique()
```

bar plot
```{r}
dodge <- position_dodge(width = 0.8)

df |>
    filter(model == "enwiki_20180420_300d") |>
    filter(implementation == "WE") |>
    filter(similarity_level == "high") |>
    filter(word_n %% 100 == 0) |>
    ggplot(aes(x = as.factor(word_n), y = cosine_similarity, fill = similarity_rank)) +
    geom_col(position = dodge) +
    facet_wrap(. ~ id, scales = "free_x", ncol = 1) +
    geom_text(
        aes(label = word),
        position = dodge,
        # vjust = -0.3,
        angle = 45
    ) +
    scale_fill_manual(values = ltc("olga")) +
    theme_bw() +
    theme(legend.position = "bottom")
```

line plot for one model colored by rank
```{r}
df |>
    filter(model == "BAAI/bge-m3") |>
    # filter(model == "enwiki_20180420_300d") |>
    # filter(implementation == "WE") |>
    filter(similarity_level == "high") |>
    filter(word_n %% 50 == 0) |>
    ggplot(
        aes(
            x = word_n,
            y = word,
            color = similarity_rank,
            group = similarity_rank
        )
    ) +
    geom_point(size = 4) +
    geom_line() +
    facet_wrap(. ~ id, scales = "free", ncol = 1) +
    scale_color_manual(values = adjust_ltc(heatmap1, amount = -5)) +
    theme_bw() +
    theme(legend.position = "bottom")
```

line plot for one model colored by word
```{r}
library(ggrepel)

df |>
    # filter(model == "Qwen/Qwen3-Embedding-8B") |>
    filter(model == "enwiki_20180420_300d") |>
    filter(implementation == "WE") |>
    filter(similarity_level == "high") |>
    filter(word_n %% 10 == 0) |>
    ggplot(
        aes(
            x = word_n,
            y = similarity_rank,
            color = word,
            group = word
        )
    ) +
    geom_point(size = 4) +
    geom_line() +
    geom_text_repel(
        data = \(x) x |>
            group_by(id, word) |>
            slice_max(word_n, n = 1),
        aes(label = word),
        direction = "y",
        hjust = 0,
        show.legend = FALSE
    ) +
    facet_wrap(~id, scales = "free", ncol = 1) +
    theme_bw() +
    theme(legend.position = "none")
```

line plot all models for one similarity rank
```{r}
df |>
    filter(similarity_rank == 1) |>
    filter(similarity_level == "high") |>
    filter(implementation != "CWE") |>
    filter(word_n %% 100 == 0) |>
    ggplot(
        aes(
            x = word_n,
            y = word,
            color = model,
            group = model
        )
    ) +
    geom_point(size = 4) +
    geom_line(size = 1, alpha = .2) +
    facet_wrap(. ~ id, scales = "free", ncol = 1) +
    scale_color_manual(values = ltc("hat")) +
    theme_bw() +
    theme(legend.position = "bottom")
```

line plot all models but one article id colored by rank
```{r}
df |>
    filter(similarity_level == "high") |>
    filter(id == 4) |>
    filter(word_n %% 100 == 0) |>
    ggplot(
        aes(
            x = word_n,
            y = word,
            color = similarity_rank,
            group = similarity_rank
        )
    ) +
    geom_point(size = 4) +
    geom_line() +
    facet_wrap(model ~ implementation, scales = "free", ncol = 2) +
    scale_color_manual(values = adjust_ltc(heatmap1, amount = -5)) +
    theme_bw() +
    theme(legend.position = "bottom")
```

line plot all models but one article id colored by rank (specified where in the text)
```{r}
df |>
    filter(similarity_level == "high") |>
    filter(id == 4) |>
    filter(word_n > 20) |>
    filter(word_n < 31) |>
    ggplot(
        aes(
            x = word_n,
            y = word,
            color = similarity_rank,
            group = similarity_rank
        )
    ) +
    geom_point(size = 4) +
    geom_line() +
    facet_wrap(model ~ implementation, scales = "free", ncol = 2) +
    scale_color_manual(values = adjust_ltc(heatmap1, amount = -5)) +
    theme_bw() +
    theme(legend.position = "bottom")
```

## plot specific words
read data
```{r}
df <- read.csv(file.path("results", "words_context_embedding_similarities.csv"))
```

```{r}
models <- df |>
    pull(model) |>
    unique()
```

line plot all models specific words one article
```{r}
words <- c(
    "wolf",
    "fox",
    "farmer",
    "threaten",
    "fetch",
    "steal",
    "devour",
    "greedy",
    "attack",
    "kill",
    "hungry"
)

df |>
    filter(id == 4) |>
    filter(word %in% words) |>
    ggplot(
        aes(
            x = word_n,
            y = cosine_similarity,
            color = word,
            group = word
        )
    ) +
    geom_line() +
    # geom_point(alpha = .1) +
    # geom_smooth() +
    facet_wrap(model ~ implementation, scales = "free", ncol = 2) +
    scale_color_manual(values = ltc("hat")) +
    theme_bw() +
    theme(legend.position = "bottom")
```

line plot all models specific words one article (w. annotations)
```{r}
words <- c(
    "pancakes",
    "lamb",
    "sheep",
    "meat"
)

# annotations
annotations <- list(
    "Eating lamb" = 54,
    "Eating pancakes" = 234,
    "Eating meat" = 477
)

annotations_df <- data.frame(
    label = names(annotations),
    word_n = unlist(annotations),
    row.names = NULL
)

df |>
    filter(id == 4) |>
    filter(word %in% words) |>
    ggplot(
        aes(
            x = word_n,
            y = cosine_similarity,
            color = word,
            group = word
        )
    ) +
    # geom_line() +
    geom_point(alpha = .1) +
    geom_smooth() +
    geom_vline(
        data = annotations_df,
        aes(xintercept = word_n),
        linetype = "dashed",
        linewidth = 0.5,
        color = "black",
        inherit.aes = FALSE
    ) +
    geom_text(
        data = annotations_df,
        aes(x = word_n, y = Inf, label = label),
        angle = 90,
        vjust = 1.2,
        hjust = 1,
        inherit.aes = FALSE
    ) +
    facet_wrap(model ~ implementation, scales = "free", ncol = 2) +
    # scale_color_manual(values = ltc("hat")) +
    theme_bw() +
    theme(legend.position = "bottom")
```