# Exploration of data from DERCo

```{r}
library(tidytable)
library(ggplot2)
library(lmerTest)

setwd("experiment2")
```

## Read data
```{r}
data_path <- file.path("data", "DERCo")
mean_amplitude <- read.csv(file.path(data_path, "mean_amplitude.csv"))
```

## Check ERPs on Cloze
```{r}
mean_amplitude |>
    filter(!level == "") |>
    mutate(level = factor(level, levels = c("low", "medium", "high"))) |>
    group_by(level) |>
    summarize(
        "n400" = mean(n400),
        "p600" = mean(p600)
    )
```

```{r}
n400_fit <- lmer(
    (n400 ~ p_cloze +
        (1 + p_cloze | subject) +
        (1 + p_cloze | article)),
    data = mean_amplitude
)

summary(n400_fit)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n400 ~ p_cloze + (1 + p_cloze | subject) + (1 + p_cloze | article))
   Data: mean_amplitude

REML criterion at convergence: 235957.9

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-4.5890 -0.6456  0.0004  0.6351  5.0707 

Random effects:
 Groups   Name        Variance  Std.Dev.  Corr  
 subject  (Intercept) 7.175e-03 8.471e-02       
          p_cloze     6.965e-03 8.346e-02 -0.11 
 article  (Intercept) 0.000e+00 0.000e+00       
          p_cloze     4.417e-09 6.646e-05  NaN  
 Residual             5.085e+00 2.255e+00       
Number of obs: 52844, groups:  subject, 22; article, 5

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)    
(Intercept) -0.03842    0.02289 21.18768  -1.679    0.108    
p_cloze      0.33055    0.03376 19.64307   9.791 5.36e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
        (Intr)
p_cloze -0.421
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
p600_fit <- lmer(
    (p600 ~ p_cloze +
        (1 + p_cloze | subject) +
        (1 + p_cloze | article)),
    data = mean_amplitude
)

summary(p600_fit)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p600 ~ p_cloze + (1 + p_cloze | subject) + (1 + p_cloze | article))
   Data: mean_amplitude

REML criterion at convergence: 224938.6

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-4.7660 -0.6446 -0.0071  0.6475  5.6886 

Random effects:
 Groups   Name        Variance  Std.Dev. Corr  
 subject  (Intercept) 0.0717262 0.26782        
          p_cloze     0.0037228 0.06102  0.20  
 article  (Intercept) 0.0002637 0.01624        
          p_cloze     0.0001652 0.01285  -1.00 
 Residual             4.1245289 2.03089        
Number of obs: 52844, groups:  subject, 22; article, 5

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)   
(Intercept) -0.03674    0.05895 21.29422  -0.623  0.53972   
p_cloze      0.10658    0.02954 14.36979   3.609  0.00274 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
        (Intr)
p_cloze -0.075
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')