# Semantic association of semantic illusions

```{r}
library(tidytable)
library(ggplot2)
library(stringr)
library(reshape2)

setwd("experiment1")
```

## Read data
```{r}
kuperberg_df <- read.csv(file.path("results", "kuperberg_semantic_association.csv")) |>
    # mutate(cond = case_when(
    #     cond == 1 ~ "a",
    #     cond == 2 ~ "b",
    #     cond == 3 ~ "c",
    #     cond == 4 ~ "d"
    # )) |>
    mutate(cond = case_when(
        cond == 1 ~ "No violation",
        cond == 2 ~ "Pragmatic non-thematic role violation",
        cond == 3 ~ "Related animacy thematic role violation",
        cond == 4 ~ "Unrelated animacy thematic role violation"
    )) |>
    mutate("cond" = factor(
        cond,
        levels = c(
            "No violation",
            "Pragmatic non-thematic role violation",
            "Related animacy thematic role violation",
            "Unrelated animacy thematic role violation"
        )
    )) |>
    filter(!scenario %in% c(37, 38, 84)) |> # scenarios with duplicate sentences
    filter(!scenario == 152) |> # non-sensible scenario
    filter(!(scenario == 230 & cond == 4)) # duplicate cond3 and cond4

kim_osterhout_df <- read.csv(file.path("results", "kim_osterhout_semantic_association.csv")) |>
    mutate("cond" = factor(condition,
        levels = c(
            "Attraction Violation",
            "Passive Control",
            "Active Control",
            "No-Attraction Violation"
        )
    ))

michaelov_df <- read.csv(file.path("results", "michaelov_semantic_association.csv")) |>
    mutate("cond" = factor(Condition,
        levels = c("BC", "Rel", "Unrel", "Implaus")
    ))

delogu_df <- read.csv(file.path("results", "delogu_semantic_association.csv")) |>
    mutate("cond" = factor(Condition,
        levels = c("control", "script-related", "script-unrelated")
    ))

delogu_nl_df <- read.csv(file.path("results", "delogu_nl_semantic_association.csv")) |>
    mutate("cond" = factor(Condition,
        levels = c("control", "script-related", "script-unrelated")
    ))

hoeks_df <- read.csv(file.path("results", "hoeks_semantic_association.csv")) |>
    mutate("cond" = condition)

exclude_imp <- c("BERTWE", "Mamba") # implementations excluded from plots
exclude_models <- c( # models excluded from plots
    "Gameselo/STS-multilingual-mpnet-base-v2",
    "bigscience/sgpt-bloom-7b1-msmarco"
)
```

## Kuperberg

### Initial exploration
By condition
```{r}
kuperberg_df |>
    group_by(cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE),
        "max" = max(semantic_association, na.rm = TRUE),
        "min" = min(semantic_association, na.rm = TRUE),
        "NAs" = sum(is.na(semantic_association))
    )
```

```{r}
kuperberg_df |>
    filter(!implementation %in% exclude_imp) |>
    filter(!model %in% exclude_models) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    mutate("implementation_f" = factor(
        implementation,
        levels = c("WE", "CWE", "SE")
    )) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation_f,
        ncol = 3,
        scales = "free_x", space = "free_x"
    ) +
    theme_bw() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 60, hjust = 1)
    ) +
    guides(color = guide_legend(nrow = 2))

ggsave(file.path("figs", "semantic_association_kuperberg.png"), width = 7, height = 5)
```

```{r}
kuperberg_df |>
    filter(implementation %in% exclude_imp) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation, ncol = 3, scales = "free") +
    theme_minimal() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

```{r}
kuperberg_df |>
    group_by(model, implementation, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    ggplot(aes(x = cond, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    facet_wrap(implementation ~ model, ncol = 3, scales = "free") +
    labs(x = "Condition") +
    theme_minimal() +
    theme(
        legend.position = "none"
    )
```

```{r}
kuperberg_df |>
    mutate("cond" = as.factor(cond)) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ggplot(aes(x = model, y = semantic_association, fill = cond)) +
    # geom_violin() +
    geom_boxplot() +
    scale_fill_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "") +
    facet_wrap(. ~ implementation, ncol = 2, scales = "free") +
    theme_minimal() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

Difference from baseline
```{r}
kuperberg_df |>
    mutate("cond" = as.factor(cond)) |>
    group_by(implementation, model, scenario) |>
    mutate(
        diff_from_baseline = `semantic_association` - `semantic_association`[cond == 1]
    ) |>
    ungroup() |>
    filter(cond != 1) |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(diff_from_baseline, na.rm = TRUE),
        "sd" = sd(diff_from_baseline, na.rm = TRUE),
        "max" = max(diff_from_baseline, na.rm = TRUE),
        "min" = min(diff_from_baseline, na.rm = TRUE)
    )
```


```{r}
kuperberg_df |>
    mutate("cond" = as.factor(cond)) |>
    group_by(implementation, model, scenario) |>
    mutate(
        diff_from_baseline = `semantic_association` - `semantic_association`[cond == 1]
    ) |>
    ungroup() |>
    filter(cond != 1) |>
    group_by(implementation, model) |>
    mutate(diff_from_baseline = scale(diff_from_baseline)) |>
    ggplot(aes(x = model, y = diff_from_baseline, fill = cond)) +
    # geom_violin() +
    geom_boxplot() +
    scale_fill_manual(
        values = c("firebrick2", "purple", "orange")
    ) +
    labs(x = "") +
    facet_wrap(. ~ implementation, scales = "free") +
    theme_minimal() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

### Correlations in estimates between models
```{r}
cor_matrix <- kuperberg_df |>
    mutate(name = paste("sem", implementation, model, sep = "_")) |>
    select(name, semantic_association, cond, scenario) |>
    pivot_wider(names_from = name, values_from = semantic_association) |>
    select(starts_with("sem_")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^sem_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)
```

```{r}
prefix_order <- c("BERTWE", "WE", "CWE", "SE")

level_order <- colnames(cor_matrix)[
    order(match(str_extract(colnames(cor_matrix), "^[^_]+"), prefix_order))
]

melted <- melt(cor_matrix) |>
    mutate(
        Var1 = factor(Var1, levels = level_order),
        Var2 = factor(Var2, levels = level_order)
    )

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```


### Semantic association in specific scenarios
```{r}
kuperberg_df |>
    filter(scenario == 56) |>
    select(target, model, implementation, semantic_association)
```

```{r}
scenario_number <- 27

kuperberg_df |>
    group_by(implementation, model) |>
    mutate(
        sem_s = scale(semantic_association),
        implementation_model = paste(implementation, model, sep = " : "),
        context_target = paste(context, target, sep = "..."),
    ) |>
    mutate(cond_sentence = paste(cond, context_target, sep = ": ")) |>
    ungroup() |>
    filter(scenario == scenario_number) |>
    ggplot(aes(x = implementation_model, y = cond_sentence, fill = sem_s)) +
    geom_tile(color = "white") +
    scale_fill_gradient2(
        low = "blue3", high = "red2", mid = "thistle1",
        na.value = "grey",
        midpoint = 0, , limit = c(-5, 5)
    ) +
    labs(y = "", x = "", fill = "semantic association") +
    theme_classic() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    ) +
    theme(aspect.ratio = .5)

kuperberg_df |>
    filter(scenario == scenario_number) |>
    select(sentences, cond)
pull(sentences) |>
    unique()
```

## Kim and Osterhout

### Initial exploration
By condition
```{r}
kim_osterhout_df |>
    group_by(cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE),
        "max" = max(semantic_association, na.rm = TRUE),
        "min" = min(semantic_association, na.rm = TRUE),
        "NAs" = sum(is.na(semantic_association))
    )
```

```{r}
# what are the sentence with NAs?
kim_osterhout_df |>
    filter(is.na(semantic_association)) |>
    select(condition, context, target, implementation)

# only active control for CWE!
```

```{r}
kim_osterhout_df |>
    filter(!implementation %in% exclude_imp) |>
    filter(!model %in% exclude_models) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    mutate("implementation_f" = factor(
        implementation,
        levels = c("WE", "CWE", "SE")
    )) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation_f,
        nrow = 3,
        scales = "free_x", space = "free_x"
    ) +
    theme_bw() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 60, hjust = 1)
    )

ggsave(file.path("figs", "semantic_association_kim_osterhout.png"), width = 7, height = 5)
```

## Michaelov

### Initial exploration
By condition
```{r}
michaelov_df |>
    group_by(cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE),
        "max" = max(semantic_association, na.rm = TRUE),
        "min" = min(semantic_association, na.rm = TRUE),
        "NAs" = sum(is.na(semantic_association))
    )
```

```{r}
michaelov_df |>
    filter(!implementation %in% exclude_imp) |>
    filter(!model %in% exclude_models) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    mutate("implementation_f" = factor(
        implementation,
        levels = c("WE", "CWE", "SE")
    )) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation_f, ncol = 3, scales = "free", space = "free_x") +
    theme_bw() +
    theme(
        legend.position = "right",
        axis.text.x = element_text(angle = 90, hjust = 1)
    )

ggsave(file.path("figs", "semantic_association_michaelov.png"), width = 8, height = 6)
```

```{r}
michaelov_df |>
    mutate("cond" = as.factor(cond)) |>
    group_by(model, implementation, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    ggplot(aes(x = cond, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    facet_wrap(implementation ~ model, ncol = 3, scales = "free") +
    labs(x = "Condition") +
    theme_minimal() +
    theme(
        legend.position = "none"
    )
```

```{r}
michaelov_df |>
    mutate("cond" = as.factor(cond)) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ggplot(aes(x = model, y = semantic_association, fill = cond)) +
    # geom_violin() +
    geom_boxplot() +
    scale_fill_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "") +
    facet_wrap(. ~ implementation, ncol = 2, scales = "free") +
    theme_minimal() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

### Correlations in estimates between models
```{r}
cor_matrix <- michaelov_df |>
    mutate(name = paste("sem", implementation, model, sep = "_")) |>
    select(name, semantic_association, cond, ContextCode) |>
    pivot_wider(names_from = name, values_from = semantic_association) |>
    select(starts_with("sem_")) |>
    cor(use = "pairwise.complete.obs")

# Remove prefix
prefix <- "^sem_"
colnames(cor_matrix) <- str_remove(colnames(cor_matrix), prefix)
rownames(cor_matrix) <- str_remove(rownames(cor_matrix), prefix)
```

```{r}
prefix_order <- c("BERTWE", "WE", "CWE", "SE")

level_order <- colnames(cor_matrix)[
    order(match(str_extract(colnames(cor_matrix), "^[^_]+"), prefix_order))
]

melted <- melt(cor_matrix) |>
    mutate(
        Var1 = factor(Var1, levels = level_order),
        Var2 = factor(Var2, levels = level_order)
    )

ggplot(melted, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    geom_text(aes(label = round(value, 2)), color = "black", size = 3) +
    scale_fill_gradient2(
        low = "blue", high = "red", mid = "white",
        midpoint = 0, limit = c(-1, 1)
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "", y = "", fill = "Correlation") +
    theme(aspect.ratio = 1)
```

### Semantic association in specific contexts
```{r}
michaelov_df |>
    filter(ContextCode == 1) |>
    select(target, model, implementation, semantic_association)
```

```{r}
context_number <- 1

michaelov_df |>
    group_by(implementation, model) |>
    mutate(
        sem_s = scale(semantic_association),
        implementation_model = paste(implementation, model, sep = " : "),
        context_target = paste(context, target, sep = "..."),
    ) |>
    mutate(cond_sentence = paste(cond, context_target, sep = ": ")) |>
    ungroup() |>
    filter(ContextCode == context_number) |>
    ggplot(aes(x = implementation_model, y = cond_sentence, fill = sem_s)) +
    geom_tile(color = "white") +
    scale_fill_gradient2(
        low = "blue3", high = "red2", mid = "thistle1",
        na.value = "grey",
        midpoint = 0, , limit = c(-5, 5)
    ) +
    labs(y = "", x = "", fill = "semantic association") +
    theme_classic() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    ) +
    theme(aspect.ratio = .5)

michaelov_df |>
    filter(ContextCode == context_number) |>
    # select(Sentence, cond)
    pull(Sentence) |>
    unique()
```

## Delogu

### Initial exploration
By condition
```{r}
delogu_df |>
    group_by(cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE),
        "max" = max(semantic_association, na.rm = TRUE),
        "min" = min(semantic_association, na.rm = TRUE),
        "NAs" = sum(is.na(semantic_association))
    )
```

```{r}
delogu_df |>
    filter(!implementation %in% exclude_imp) |>
    filter(!model %in% exclude_models) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    mutate("implementation_f" = factor(
        implementation,
        levels = c("WE", "CWE", "SE")
    )) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation_f,
        nrow = 3,
        scales = "free_x", space = "free_x"
    ) +
    theme_bw() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 60, hjust = 1)
    )

ggsave(file.path("figs", "semantic_association_delogu.png"), width = 7, height = 5)
```

## Delogu (NL translation)

### Initial exploration
By condition
```{r}
delogu_nl_df |>
    group_by(cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE),
        "max" = max(semantic_association, na.rm = TRUE),
        "min" = min(semantic_association, na.rm = TRUE),
        "NAs" = sum(is.na(semantic_association))
    )
```

```{r}
delogu_nl_df |>
    filter(!implementation %in% exclude_imp) |>
    filter(!model %in% exclude_models) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    mutate("implementation_f" = factor(
        implementation,
        levels = c("WE", "CWE", "SE")
    )) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation_f,
        nrow = 3,
        scales = "free_x", space = "free_x"
    ) +
    theme_bw() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 60, hjust = 1)
    )

ggsave(file.path("figs", "semantic_association_delogu_nl.png"), width = 7, height = 5)
```

## Hoeks

### Initial exploration
By condition
```{r}
hoeks_df |>
    group_by(cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE),
        "max" = max(semantic_association, na.rm = TRUE),
        "min" = min(semantic_association, na.rm = TRUE),
        "NAs" = sum(is.na(semantic_association))
    )
```

```{r}
hoeks_df |>
    filter(!implementation %in% exclude_imp) |>
    filter(!model %in% exclude_models) |>
    group_by(implementation, model) |>
    mutate(semantic_association = scale(semantic_association)) |>
    ungroup() |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    mutate("implementation_f" = factor(
        implementation,
        levels = c("WE", "CWE", "SE")
    )) |>
    ggplot(aes(x = model, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "", color = "Condition") +
    facet_wrap(. ~ implementation_f,
        nrow = 3,
        scales = "free_x", space = "free_x"
    ) +
    theme_bw() +
    theme(
        legend.position = "right",
        axis.text.x = element_text(angle = 90, hjust = 1)
    )

ggsave(file.path("figs", "semantic_association_hoeks.png"), width = 8, height = 6)
```

## Test BERT
```{r}
test <- read.csv(file.path("results", "test_BERT.csv"))
```

```{r}
test |>
    mutate("cond" = as.factor(cond)) |>
    group_by(implementation, model, cond) |>
    summarize(
        "mean" = mean(semantic_association, na.rm = TRUE),
        "sd" = sd(semantic_association, na.rm = TRUE)
    ) |>
    ggplot(aes(x = implementation, color = cond, group = cond)) +
    geom_point(
        aes(y = mean),
        position = position_dodge(width = 0.3),
        size = 2
    ) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = 0.15,
        position = position_dodge(width = 0.3)
    ) +
    scale_colour_manual(
        values = c("blue", "firebrick2", "purple", "orange")
    ) +
    labs(x = "") +
    theme_minimal() +
    theme(
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```